---
output: github_document
---

# Preci_diasg: Temporal downscaling of precipitation.
  
*PreciTDS* package generates a higher resolution temporal scale (15-min) from 1-h precipitation using a modified stochastic disaggregation method.

# Installation:

The package can be installed from [github](https://github.com/bijoychandraAU/PreciTDS)

```{r eval=FALSE}
list.of.packages <- c("devtools")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(devtools)
#install_github("bijoychandraAU/PreciTDS")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction:

*PreciTDS* package required both observed (15-min) and model (1-h) precipitation data. Both precipitation can be either continuous or discontinuous time series format. They have to be either dataframe or tibble format. 

## Example:

The projected precipitation for 1 year (2030) that recorded at 1-h scale is disaggregated to 15-min precipitation using the observed 15-min precipitation.  

### 1. Observed 15-min (O15) precipitation.

```{r observed, eval=FALSE}
library(PreciTDS)
data(observed,package = "PreciTDS")
head(observed,5)
```

### 2. Model 1-hour (DS60) precipitation.

```{r model, eval=FALSE}
data(model,package = "PreciTDS")
head(model,5)
```

### 3. Disaggregated 15-min (DS15) preicptiation from DS60.

```{r eval=FALSE}
DS15=Preci_diasg(obs=observed,mod=model)
head(DS15,5)
```


# References:
 - Choi, J., Socolofsky, S. A. & Olivera, F. [Hourly disaggregation of daily rainfall in Texas  using measured hourly precipitation at other locations](https://doi.org/10.1061/(ASCE)1084-0699(2008)13:6(476)). Journal of Hydrologic 575 Engineering 13, 476–487 (2008).
 
 - Socolofsky, S., Adams, E. E. & Entekhabi, D. [Disaggregation of daily rainfall for  continuous watershed modeling](https://doi.org/10.1061/(ASCE)1084-0699(2001)6:4(300)). Journal of Hydrologic Engineering 6, 300–309 (2001).
 
 - Mirhosseini, G., Srivastava, P. & Stefanova, L.[The impact of climate change on rainfall  Intensity–Duration–Frequency (IDF) curves in Alabama](https://doi.org/10.1007/s10113-012-0375-5). Reg Environ Change 13, 25–33 519 (2013).

# Authors:
 - [Bijoychandra Takhellambam](https://github.com/bijoychandraAU)
 - Puneet Srivastava
 - Jasmeet Lamba
 - Ryan P. McGehee
 - Hemendra Kumar
 - Di Tian
  

